Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
Revise corpus references

\textbf{The Unified
  Model}~\cite{um-website}
is a weather forecasting and climate modelling tool developed by the
Met Office in the United Kingdom. It is used by research organisations
and meteorological services around the world. We use the development
branch (trunk) of the model. The code based in closed source but
institutional licenses are available for research purposes. The Met Office runs a comprehensive code quality system incorporating dedicated committers (we counted 11) for particular parts of the model. We counted 120 additional contributors whose submissions are reviewed and tested before being accepted into the code base.

@@

\textbf{BLAS} (Basic Linear Algebra Subprograms)\footnote{\url{http://www.netlib.org/blas/}} provides efficient and portable routines for vector and matrix operations. These routines feature in many other libraries (including LAPACK). We used version 3.6.0.

@@

\textbf{GEOS-Chem}\footnote{\url{http://acmg.seas.harvard.edu/geos/}} is a three-dimensional model of tropospheric chemistry developed at Harvard and used by approximately 70 universities and research institutions world-wide. We examined version 10-01.

>>>>

\textbf{The Unified
  Model}~\cite{um}
is a weather forecasting and climate modelling tool developed by the
Met Office in the United Kingdom. It is used by research organisations
and meteorological services around the world. We use the development
branch (trunk) of the model. The code based in closed source but
institutional licenses are available for research purposes. The Met Office runs a comprehensive code quality system incorporating dedicated committers (we counted 11) for particular parts of the model. We counted 120 additional contributors whose submissions are reviewed and tested before being accepted into the code base.

@@

\textbf{BLAS}~\cite{blas} (Basic Linear Algebra Subprograms) provides efficient and portable routines for vector and matrix operations. These routines feature in many other libraries (including LAPACK). We used version 3.6.0.

@@

\textbf{GEOS-Chem}~\cite{geos-chem} is a three-dimensional model of tropospheric chemistry developed at Harvard and used by approximately 70 universities and research institutions world-wide. We examined version 10-01.
